Verifying Demonstrations

### 2019-02-13 paper/intro.tex
Edits outline

The paper is organized as follows.
First, in \cref{system-model}, we describe our system model and summarize the desired properties for crowd counting. Next, in \cref{related-work}, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \CROCUS. 
We then formalize the notion of protest and the desired verifiability and privacy properties, and in \cref{building-blocks}, we give the relevant background on the building blocks of our solution. 
Afterwards, in \cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, different from that originally proposed by \textcite{DistanceBounding}.
We provide a proof of its security (\ie the fact that it achieved all desired \ac{DB} properties) 
\daniel{Check that this is true before publication.} 
and formally verify it using Tamarin~\cite{TamarinDB}.
\seb{we need to be careful about the above sentence}
%This version of the Schnorr protocol can then be used to do general \ac{DB} anonymous credentials.
Then in \cref{Protocol}, we present \CROCUS, a privacy-preserving crowd 
counting estimation protocol constructed from these building blocks, before 
analyzing its security and privacy (\cref{SecurityAnalysis}).
Finally, we discuss our assumptions and results \cref{Discussion} and give our conclusions in \cref{Conclusion}.
%\sonja{add (sub) sections for performance and verification}

>>>>

The paper is organized as follows.
\Cref{system-model}, we describe our system model and summarize the desired 
properties for crowd counting.
We then discuss related work in terms of these properties in 
\cref{related-work}:
we first discuss the crowd counting methods that are classically used, then 
work on location proof systems and, finally, some work on distance bounding.

\Cref{definitions}, we formalize the notion of protest and the desired 
verifiability and privacy properties, and in \cref{building-blocks}, we give 
the relevant background on the building blocks of our solution.

\Cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, 
different from that originally proposed by \textcite{DistanceBounding}.
We provide a proof of its security and formally verify it using 
Tamarin~\cite{TamarinDB}.

\Cref{Protocol}, we present \CROCUS, a privacy-preserving crowd counting 
estimation protocol.
We analyze its security in \cref{SecurityAnalysis} and estimate its performance 
in \cref{PerformanceAnalysis}.

Finally, we discuss our assumptions and results in \cref{Discussion} and give 
our conclusions in \cref{Conclusion}.
